---
title: "American Samoa Child Coverage and Vaccination Planning"
author: "USAPI Assessment Team | Surveillance & Epidemiology Branch | ISD | NCIRD | CDC"
date: today
date-format: long
params:
  age_as_of_date: null
format:
  html:
    theme: flatly
    toc: true
    toc-depth: 2
    code-fold: true
    css: ../www/styles.css
execute:
  warning: false
  message: false
  echo: false
---

This analysis links the American Samoa WebIZ roster, Patient Details with
Services, and Reminder/Recall reports. It assigns census geography, evaluates
children aged 2-83 months, exports the eight planning tables, and refreshes the
Shiny dashboard. Set the reporting date and input/product choices in `config.R`.
For a direct run with live Console progress, open `RUN_ANALYSIS.R` and click
**Source** instead of rendering this report. The Quarto progress bar stays on
run-analysis while the pipeline works; stage and child-count messages show
progress in the Render pane.

```{r}
#| label: run-analysis
#| include: false
here::i_am("analysis/American_Samoa_Child_Coverage_Planning_Analysis.qmd")
source(here::here("R", "run_analysis.R"), local = TRUE)
result <- run_as_analysis(analysis_date = params$age_as_of_date)
```

## Input reports

```{r}
knitr::kable(data.frame(Report = names(result$input_files),
  File = basename(result$input_files), row.names = NULL))
```

The newest matching reports are selected when no paths are specified. Filenames
may start with `Roster`, `Details`/`Detail`, or `RR`; full report names containing
Patient Roster, Patient Details with Services, Reminder, or Recall also work.

## Geography

Reminder/Recall **City** supplies residence. Its IIS label is matched to the
workbook's official census designation. Raw County in either patient report is
ignored. If the city is unrecognized or its county is ambiguous, the roster
clinic may identify a county. A clinic county does not establish a child's
village. Unresolved and combined geographies remain labeled and appear in QA.

Population, under-age-5 population, area, and density come from the supplied
2020 Census workbook. Locality aliases share their official parent village's
statistics; these values are not summed across patient records or aliases.

## Vaccine status and planning

The assessment uses the first routine age anchor. DTaP dose 4 begins at 15
months; MMR and varicella dose 2 begin at 48 months. Hib/PCV requirements depend
on the ages and types of previous valid doses. Healthy children aged 60 months
or older have no routine Hib/PCV catch-up need and are excluded from those
eligible denominators. HepA dose 2 uses a six-calendar-month interval.

Rotarix uses two doses; RotaTeq or mixed/unknown histories use three. Age limits
prevent new rotavirus doses after eight months. Core UTD retains the CNMI
eight-antigen measure, with rotavirus shown separately. This core measure does
not include seasonal or medical-risk schedules.

**Not UTD** and **eligible for a dose today** are separate measures. Product
estimates cover one eligible visit, not all future doses needed to complete
each series. Combinations are selected only when all included antigens are
eligible. Change product preferences to match local inventory after reviewing
the audit below.

Sources: [AAP 2026 schedule, updated September 2, 2026](https://downloads.aap.org/AAP/PDF/AAP-Immunization-Schedule.pdf),
[CDC PedvaxHIB catch-up](https://www.cdc.gov/vaccines/hcp/imz-schedules/downloads/job-aids/hib-pedvax.pdf),
[CDC other/mixed Hib catch-up](https://www.cdc.gov/vaccines/hcp/imz-schedules/downloads/job-aids/hib-acthib.pdf),
and [CDC PCV catch-up](https://www.cdc.gov/vaccines/hcp/imz-schedules/downloads/job-aids/pneumococcal.pdf).

## Run QA

```{r}
knitr::kable(result$run_qa)
```

## Combination vaccine use

This is measured from the selected Patient Details with Services report after
excluding non-administrations, missing dates, future administrations, and
duplicate patient/date/CVX records. CVX 130 does not distinguish Kinrix from
Quadracel. Frequencies describe recorded use and do not establish current stock.

```{r}
knitr::kable(result$product_audit[result$product_audit$combination, ], digits = 1)
```

## Output files

```{r}
knitr::kable(data.frame(Output = names(result$paths), File = basename(result$paths), row.names = NULL))
```

The formatted workbook includes IIS Denominator, Reminder by Village, Needs by
Vaccine, Products Needed, Dose Coverage, UTD by Village, Coverage 19-35 Months,
and Series 19-35 Months, plus QA/audit tabs. Dose Coverage uses vaccine section
headings and the seven requested columns. UTD by Village summarizes the full
2-83-month population without an extra Age Group column.

Open `app.R` and run the Shiny app after this analysis completes.
